---
title: "Agent Based Modelling:Age_Structured modelling"
author: "Oluchukwu Okorie"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
This is a classwork to get graduation/maturation age
Using a function where the data can be put as an arguement which has a default data 
as the corresponding mid class point of different age groups in Nigeria and the percentile in Nigeria(Nte:Take a look at the age strata file in this project) and use it to fit  a data into a simple SIRS compartmental model and then fit to an agent-based Age Structured modelling

### Loading the required Library and loading the data already present in this folder,Note since we are using a Rproject file we don't need to set working directory

```{r cars}
getwd()#Just to show the beauty of Rproject no need to set working directory
library(minpack.lm)
library(deSolve)
library(readxl)
demography <- read_excel("demography.xls")
data <- read_excel("data.xls")
```
### Setting the default parameters
where Lambda is the recruitment into the 
```{r}
Lamda = 3000;
mu = 1/840;
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
