---
title: "Agent Based Modelling:Age_Structured modelling"
author: "Oluchukwu Okorie"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
This is a classwork to get graduation/maturation age
Using a function where the data can be put as an arguement which has a default data 
as the corresponding mid class point of different age groups in Nigeria and the percentile in Nigeria(Note:Take a look at the age strata file in this project) and use it to fit  a data into a simple SIRS compartmental model and then fit to an agent-based Age Structured modelling

## Agent-based Modelling
ABM is inherently mechanistic because it models the underlying mechanisms and interactions at the individual level to understand how they lead to emergent phenomena at the population level

### Loading the required Library and loading the data
Note the data is already present in this folder,Note since we are using a R project file we don't need to set working directory

```{r cars}
getwd()#Just to show the beauty of Rproject no need to set working directory
library(minpack.lm)
library(deSolve)
library(readxl)
demography <- read_excel("demography.xls")
data <- read_excel("data.xls")
```
### Naming the outputs needed(Incidence in children and adults)
```{r}
time <- data$`Time(Month)`;
Childeren_Incidence = data$`Under 10`;
Adult_Incidence = data$`Above 10`
Incidence = Adult_Incidence + Childeren_Incidence
```
### Ploting the Total incidence over time
```{r}
plot(time, Incidence, type = 'l', col = "red")
#legend(time,Incidence,legend)#go to seg
```

### Computing the percentile for each group
```{r}
percentile = cumsum(demography$percentages)
```
### Naming the upper bound and lower bound
```{r}
##age
lb = demography$lb
ub = demography$ub
age = 0.5*(lb[2:length(lb)] + ub[1:length(ub)-1])
```
## Modelling proper
### Initiating values
```{r}

N0 = 2503200;
I0 = 10;
S0 = N0 - I0;
R0 = 0;
Inc0 = 0
initialstate <- c(S0, I0, R0, Inc0);

```

### Setting the default parameters
where Lambda is the recruitment into the general population
```{r}
Lamda = 3000;
mu = 1/840;
```
### Defining our SIRS model
```{r}
SIRS <- function(t, state, parameters){
  beta = parameters[1];
  gamma = parameters[2];
  omega = parameters[3];
  
  S = state[1];
  I = state[2];
  R = state[3];
  N = S + I + R;
  
  dSdt = Lambda - beta*I*S/N + omega*R - mu*S;
  dIdt = beta*I*S/N - gamma*I - mu*I;
  dRdt = gamma*I - omega*R - mu*R;
  dIncdt = beta*I*S/N;
  list(c(dSdt, dIdt, dRdt, dIncdt));
}
```
## Model Estimator
Here we try to output the curve we are to use to fit the Model,using "<<" we can then 
output the ode estimator output (out) and the ode incidence a.k.a the mechanistic curve
(i.e the Mechanistic_inc variable) to the global scope
```{r}
ModelEstimator <- function(beta, gamma, omega){
  out <<-ode(initialstate, c(0, time), SIRS, c(beta, gamma, omega))
  Mechanistic_inc <<- diff(out[,5])
}

```
### plotting the mechanistic incidence
```{r}

#plot(time,Mechanistic_inc,col ="green")
```

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
